 

### 2023-03-02 paper1.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

The research draws exclusively on secondary country-level data reported at the national or subnational level. As such, it does not involve data collection, experimentation, or investigation concerning human subjects. The Institutional Review Board (IRB) of the Harvard T.H. Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB20-1946, determined on November 13, 2020).

>>>>

The research draws exclusively on secondary country-level data reported at the national or subnational level. As such, it does not involve data collection, experimentation, or investigation concerning human subjects. The Institutional Review Board (IRB) of the Harvard T.H. Chan School of Public Health determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB20-1946, determined on November 13, 2020).

### 2023-03-02 paper2.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

# Loading libraries
# library(MASS) # We load this and then detach it just to clear the package
# library(margins) # We load this and then detach it just to clear the package
# library(lme4) # We load this and then detach it just to clear the package
# detach("package:lme4", unload=TRUE) # Needed to use dplyr's select function
# detach("package:margins", unload=TRUE) # Needed to use dplyr's select function
# detach("package:MASS", unload=TRUE) # Needed to use dplyr's select function
library(readxl)
library(readr)
library(dplyr)
library(zoo)
library(tidyr)
library(psych)
library(ggplot2)
library(RColorBrewer)
library(sp)
library(broom)
library(sf)
library(scales)
library(viridis)
library(data.table)
library(ggpubr)
library(ggmap)
library(maps)
library(mapdata)
library(ggrepel)
library(table1)
library(stringr) 
library(stringi)
library(fixest)
library(stats)
library(lubridate)
library(forecast)
library(gtools)
# library(devtools)
library(reticulate)
library(stargazer)
library(lwgeom)
if (!require("ggsflabel")) devtools::install_github("yutannihilation/ggsflabel")
library(openxlsx)
library(gganimate)
library(transformr)
library(huxtable)
library(ggtext)
library(margins)
library(ncdf4) # package for netcdf manipulation
library(magrittr)
library(lmtest)
library(sandwich)
library(rgee)
library(gt)
library(knitr)
library(webshot2)
library(sysfonts)
library(showtext)
font_add_google("Source Sans Pro")
library(gridExtra)
library(tibble)
showtext_auto() 
showtext_opts(dpi = 300)  
# library(googledrive)
# drive_auth(email = TRUE)
library(rmdHelpers)
library(gtExtras)
library(kableExtra)
library(DescTools)
library(rvest)
library(httr)
library(polite)
library(janitor)
library(cowplot)
library(ggridges)
library(elevatr)
library(raster)
library(rayshader)

@@

# map_mdg_0 <- map_mdg_0 %>%
#   st_as_sf(crs= crsLONGLAT)

@@

# Get the spatial extent of the shapefile

@@

# Get the spatial extent of the PNG image
madagascar_map_bbox <- c(xmin = 0, ymin = 0, xmax = ncol(madagascar_topo_map), ymax = nrow(madagascar_topo_map))

# Calculate the scaling factor for the x-axis
x_scale_factor <- diff(madagascar_bbox[c("xmin", "xmax")]) / diff(madagascar_map_bbox[c("xmin", "xmax")])

# Calculate the scaling factor for the y-axis
y_scale_factor <- diff(madagascar_bbox[c("ymin", "ymax")]) / diff(madagascar_map_bbox[c("ymin", "ymax")])

# Extract minimum and maximum longitude and latitude
min_lon <- as.numeric(bbox["xmin"])
max_lon <-  as.numeric(bbox["xmax"])
min_lat <-  as.numeric(bbox["ymin"])
max_lat <-  as.numeric(bbox["ymax"])

@@

@@

\vspace*{\fill}

@@

@@

  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  geom_sf(alpha = 0.5, aes(color = source)) +
  theme_void() +
  theme(text = element_text(size = 16, family = "Source Sans Pro"),
        legend.position = "left") +
  scale_color_manual(values = c(col_centroid,
                                col_exact_all,
                                col_exact_rhino,
                                col_exact_val,
                                col_search),
                     name = "GPS type")

@@

  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  geom_sf(alpha = 0.5, aes(color = clinic_type_clean)) +
  theme_void() +
  theme(text = element_text(size = 16, family = "Source Sans Pro"),
        legend.position = "right") +
  scale_color_manual(values = c(col_CSB,
                                col_CHD,
                                col_CHR),
                     name = "Facility type")

@@

panel_a <- data_climate_subset %>%
  dplyr::select(date, facility_ID, mean_2m_air_temperature) %>%
  unique() %>%
  inner_join(., facilities_all_gps) %>%
  dplyr::select(date, geometry, facility_ID, mean_2m_air_temperature) %>%
  filter(date == "Jan 2015" | date == "June 2015" ) %>%
  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
  filter(!is.na(date_2)) %>%
  ggplot(aes(geometry=geometry)) +
  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = "grey40",
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_lightest) +
  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
  geom_sf(alpha = 0.9, size = .7, aes(color = mean_2m_air_temperature)) +
  theme_void() +
  # scale_alpha(range = c(0,1)) +
  scale_color_viridis(option = "magma") +
  labs(color = "Temperature ( ̊ C)") +
  theme(text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")) +
  facet_wrap(~date_2)

panel_b <-  data_climate_subset %>%
  dplyr::select(date, facility_ID, sm_mean) %>%
  unique() %>%
  inner_join(., facilities_all_gps) %>%
  dplyr::select(date, geometry, facility_ID, sm_mean) %>%
  filter(date == "Jan 2015" | date == "June 2015" ) %>%
  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
  filter(!is.na(date_2)) %>%
  ggplot(aes(geometry=geometry)) +
  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = "grey40",
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_lightest) +
  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
  geom_sf(alpha = 0.9, size = .9, aes(color = sm_mean)) +
  theme_void() +
  # scale_alpha(range = c(0,1)) +
  scale_color_viridis(option = "mako", direction = -1) +
  labs(color = "Soil moisture (%)") +
  theme(text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")) +
  facet_wrap(~date_2)

@@

>>>>

# Loading libraries
# library(MASS) # We load this and then detach it just to clear the package
# library(margins) # We load this and then detach it just to clear the package
# library(lme4) # We load this and then detach it just to clear the package
# detach("package:lme4", unload=TRUE) # Needed to use dplyr's select function
# detach("package:margins", unload=TRUE) # Needed to use dplyr's select function
# detach("package:MASS", unload=TRUE) # Needed to use dplyr's select function
library(readxl)
library(readr)
library(dplyr)
library(zoo)
library(tidyr)
library(psych)
library(ggplot2)
library(RColorBrewer)
library(sp)
library(broom)
library(sf)
library(scales)
library(viridis)
library(data.table)
library(ggpubr)
library(ggmap)
library(maps)
library(mapdata)
library(ggrepel)
library(table1)
library(stringr) 
library(stringi)
library(fixest)
library(stats)
library(lubridate)
library(forecast)
library(gtools)
# library(devtools)
library(reticulate)
library(stargazer)
library(lwgeom)
if (!require("ggsflabel")) devtools::install_github("yutannihilation/ggsflabel")
library(openxlsx)
library(gganimate)
library(transformr)
library(huxtable)
library(ggtext)
# library(margins)
library(ncdf4) # package for netcdf manipulation
library(magrittr)
library(lmtest)
library(sandwich)
library(rgee)
library(gt)
library(knitr)
library(webshot2)
library(sysfonts)
library(showtext)
font_add_google("Source Sans Pro")
library(gridExtra)
library(tibble)
showtext_auto() 
showtext_opts(dpi = 300)  
# library(googledrive)
# drive_auth(email = TRUE)
library(rmdHelpers)
library(gtExtras)
library(kableExtra)
library(DescTools)
library(rvest)
library(httr)
library(polite)
library(janitor)
library(cowplot)
library(ggridges)
library(elevatr)
library(raster)
library(rayshader)

@@

library(elevatr)
library(rayshader)
library(raster)

@@

@@

# # Get the spatial extent of the PNG image
# madagascar_map_bbox <- c(xmin = 0, ymin = 0, xmax = ncol(madagascar_topo_map), ymax = nrow(madagascar_topo_map))
# 
# 
# # Calculate the scaling factor for the x-axis
# x_scale_factor <- diff(madagascar_bbox[c("xmin", "xmax")]) / diff(madagascar_map_bbox[c("xmin", "xmax")])
# 
# # Calculate the scaling factor for the y-axis
# y_scale_factor <- diff(madagascar_bbox[c("ymin", "ymax")]) / diff(madagascar_map_bbox[c("ymin", "ymax")])
# 
# 
# # Extract minimum and maximum longitude and latitude
# min_lon <- as.numeric(bbox["xmin"])
# max_lon <-  as.numeric(bbox["xmax"])
# min_lat <-  as.numeric(bbox["ymin"])
# max_lat <-  as.numeric(bbox["ymax"])

@@

\vspace{8pt}

@@

@@

```
\newpage

@@

  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  geom_sf(alpha = 0.5, aes(color = source)) +
  theme_void() +
  theme(text = element_text(size = 16, family = "Source Sans Pro"),
        legend.position = "left") +
  scale_color_manual(values = c(col_centroid,
                                col_exact_all,
                                col_exact_rhino,
                                col_exact_val,
                                col_search),
                     name = "GPS type")

@@

  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  geom_sf(alpha = 0.5, aes(color = clinic_type_clean)) +
  theme_void() +
  theme(text = element_text(size = 16, family = "Source Sans Pro"),
        legend.position = "right") +
  scale_color_manual(values = c(col_CSB,
                                col_CHD,
                                col_CHR),
                     name = "Facility type")

@@

panel_a <- data_climate_subset %>%
  dplyr::select(date, facility_ID, mean_2m_air_temperature) %>%
  unique() %>%
  inner_join(., facilities_all_gps) %>%
  dplyr::select(date, geometry, facility_ID, mean_2m_air_temperature) %>%
  filter(date == "Jan 2015" | date == "June 2015" ) %>%
  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
  filter(!is.na(date_2)) %>%
  ggplot(aes(geometry=geometry)) +
  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  # geom_sf(data = map_mdg_2_un,
  #         size = 0.2,
  #         color = "grey40",
  #         fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_lightest) +
  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
  geom_sf(alpha = 0.9, size = .7, aes(color = mean_2m_air_temperature)) +
  theme_void() +
  # scale_alpha(range = c(0,1)) +
  scale_color_viridis(option = "magma") +
  labs(color = "Temperature ( ̊ C)") +
  theme(text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")) +
  facet_wrap(~date_2)

panel_b <-  data_climate_subset %>%
  dplyr::select(date, facility_ID, sm_mean) %>%
  unique() %>%
  inner_join(., facilities_all_gps) %>%
  dplyr::select(date, geometry, facility_ID, sm_mean) %>%
  filter(date == "Jan 2015" | date == "June 2015" ) %>%
  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
  filter(!is.na(date_2)) %>%
  ggplot(aes(geometry=geometry)) +
  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  # geom_sf(data = map_mdg_2_un,
  #         size = 0.2,
  #         color = "grey40",
  #         fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_lightest) +
  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
  geom_sf(alpha = 0.9, size = .9, aes(color = sm_mean)) +
  theme_void() +
  # scale_alpha(range = c(0,1)) +
  scale_color_viridis(option = "mako", direction = -1) +
  labs(color = "Soil moisture (%)") +
  theme(text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")) +
  facet_wrap(~date_2)

@@

```
\end{spacing}{1.5}
